### 2019-08-13 thesis.tex
*** empty log message ***

The fundamental questions of heliophysics start right in the Sun and the
magnetic dynamo processes involved in the generation and variability of
magnetic fields in the Sun, and how it determines the dynamics of the
11-year solar cycle of sunspots. The appearance of sunspots is a sign of
solar activity, characterized by solar flares and coronal mass ejections.

This enhanced flux of energetic particles and radiation have direct impact
in the \emph{space weather} around Earth, triggering geomagnetic storms
that

Inside the heliosphere, the Sun, the space environment around Earth and the
interplanetary medium are extensively explored by space probes.
%% say something about it

>>>>

The ultimate goal of heliophysics can be summarized as the search for a
better understanding of the solar dynamics and how it affects the Earth,
other planetary bodies, and the interstellar medium. The heliosphere is
a coupled system, where different interacting elements that might look
unrelated at first sight are connected by underlying plasma processes
\cite{NAP13060}. A great example of this interconnection is the relation
between the appearance of sunspots and the occurrence of non-recurrent
geomagnetic storms, which are the most intense space weather disturbances.
Evidence of such relationship started to appear at the end of the $19$th
century. The correct hypothesis (coronal mass ejections associated with
solar flares), however, which depended on advances in plasma physics
theory, came along only in $1929$ \cite{chapman1929cosmical,Koskinen2011}.

A better comprehension of the Sun and the dynamic space around our planet
goes beyond the pure scientific curiosity. It is true that this accessible
space physics laboratory can lead to discoveries that can be applied and
extended to remote cosmic systems. But the primary reason behind the
international effort (see Figures \ref{nasa} and \ref{esa}) on understanding
the complex physics of the Sun and the interplanetary space, is to enable
means to predict the occurrence and intensity of solar activity. This may
open the possibility of developing reliable space-weather forecasts that
may help us to protect satellites, humans

\begin{itemize}
\item The magnetic dynamo processes involved in the generation and variability
  of magnetic fields in the Sun, and how it determines the dynamics of the
  11-year solar cycle of solar activity \cite{Charbonneau2005};
\item The role of magnetic reconnection in the coronal mass ejection process
  \cite{Qiu2005};
\item The coronal heating problem \cite{Vinas2000,PP14,Pezzi2017};
\item   
\end{itemize}
